% BEÁLLÍTÁSOK - JOBB NEM VÁLTOZTATNI
\documentclass[final]{ubb_dolgozat}
\usepackage{definitions}

% pszeudokód írás végett
\usepackage{algpseudocode}
\usepackage[chapter]{algorithm}

% képek miatt
% \usepackage[justification=centering]{caption}
\usepackage{subcaption}
\captionsetup[table]{skip=10pt}
\captionsetup{subrefformat=parens}

% táblázatok
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{multirow}

% listák
\usepackage[shortlabels]{enumitem}

% hasznos rövidítések
\providecommand{\abs}[1]{\lvert#1\rvert}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\providecommand{\keywords}[1]
{
  \small
  \textbf{\textit{Keywords:}} #1
}

% milyen nyelveken akarunk forráskódot megjeleníteni
\lstloadlanguages{Python}
% más lehetőségek:
% C, Matlab, Mathematica, Octave, Pascal, Perl, Python
% SCilab, SQL, Haskell, Lisp, Lua, make, ML, PHP, Prolog
%
% a teljes lista a LISTINGS csomagban.


% ezt be lehet tenni MINDEGYIK megjelenítendő kód elé opcióként
\lstset{language=Python}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%!!          EZT KELL VÁLTOZTATNI       !!%%%%
%%     A DOLGOZAT CÍMOLDALÁNAK ELEMEI        %%

%% MELYIK ÉVBEN ADJUK LE
\submityear{%
2020
}

\titleHU{%
Kritikus csomópontok meghatározása komplex hálózatokban
}

% Az alábbi sorokat ki kell tölteni!

\titleEN{%
Critical node detection problem in complex networks
}

\titleRO{%
Identificarea nodurilor critice în rețele complexe
}

\author{%
Béczi Eliézer
}

%%
\tutorHU{%
dr. Gaskó Noémi,\newline egyetemi docens\\
% a hozzátartozás akkor szükséges, ha NEM BBTE-s a tanár
%{\large Babe\c{s}--Bolyai Tudományegyetem,\\
% Matematika és Informatika Kar}% ha különbözik, akkor fel kell tűntetni
}
%%
\tutorRO{%
Conf. dr. Gaskó Noémi\\
% az egyetem akkor szükséges, ha nem BBTE-s a tanár, a minta a BBTE-t
% tartalmazza
% {\large Universitatea Babe\c{s}--Bolyai,\\ % dacã diferã!!!
% Facultatea de Matematic\u{a} \c{s}i Informatic\u{a} }%
}
%%
\tutorEN{%
Assoc. prof. dr. Gaskó Noémi
% {\large Babe\c{s}--Bolyai University,\\
% Faculty of Mathematics and Informatics}
}


% 
%\includeonly{bevezet}


\begin{document}

% ez a címoldal része
\maketitle

%% ABSTRACT
\begin{abstractEN} % ANGOL VÁLTOZAT
  {
    \vfill
    The purpose of this thesis is to address the critical node detection problem (CNDP).
    The CNDP is an optimization problem that consists of finding a subset of nodes that if removed from the graph will greatly decrease the connectivity of the network.
    We approach the problem from two different perspectives: from a single-objective and a bi-objective standpoint.
    The single-objective formulation of the CNDP aims to minimize the pairwise connectivity of the graph, whereas the goal of the bi-objective one (BOCNDP) is to maximize the number of connected components while simultaneously minimizing the variance of their cardinalities.
    For solving the CNDP we propose three different algorithms: a greedy, a genetic and a memetic algorithm.
    In the case of the BOCNDP, we use six common MOEAs (NSGA-II, PAES etc.), and experiment with different dominance operators, such as Pareto-, Nash- and Berge-dominance.
    Finally, we give a brief comparison of the algorithms using a benchmark set that contains four groups of graphs with different characteristics (Barabási–Albert, Erdős–Rényi etc.).
    \\[.5cm]
    \keywords{
      complex networks,
      critical node detection problem,
      single-objective,
      bi-objective,
      evolutionary algorithms,
      game theory
    }
    \vfill
  }
  \vspace*{.5cm}
  This work is the result of my own activity. I have neither given nor received unauthorized assistance on this work.
\end{abstractEN}

% a dolgozat tartalomjegyzéke -- ez automatikusan generálódik a STRUKTÚRA alapján.
{
\baselineskip 1ex
\parskip 1ex
\tableofcontents
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%         a dolgozat tartalma         %%%%%%%%%%%%

% ajánlott külön file-okba írni az egyes fejezeteket,
% ugyanis úgy jobban át lehet látni.


% a bevezető fejezet FILE-ja.
\include{bevezet}

% saját fejezetek
\include{chapters/introduction/introduction}
\include{chapters/single-objective-cndp/single-objective-cndp}
\include{chapters/bi-objective-cndp/bi-objective-cndp}
\include{chapters/conclusions/conclusions}

{ \renewcommand{\baselinestretch}{0.8}
  \normalsize
  \setlength{\itemsep}{-2.4mm}
  \setlength{\bibspacing}{0.67\baselineskip}
  \bibliographystyle{abbrvnat_hu}
  \bibliography{dolgozat}
}

\end{document}
